Physical Implementation of Quantum Computers

### 2023-07-07 article.tex
Small corrections

\begin{abstract}
  This work aims to explain the physical principles of quantum computers. We will discuss how some physical systems can be used to peform computation, specialy with respect to three chosen impleentations, as well as the main advantages and disadvantages of each implementation.
  The implementations we will discuss are ion traps, photonic models and solid state systems. The ion trap model revolves around the manipulation of ions confined within a trap, while the photonic model centers on the manipulation of photons within a cavity, and the solid-state model focuses on the manipulation of electrons within a superconducting circuit.
  The main advantages and disadvantages of each model are presented, as well as the main challenges for the construction of a quantum computer.

@@

In this work we will discuss the physical principles of quantum computers. We will discuss how some physical systems can be used to peform computation~\ref{sec:physical_properties}, specialy with respect to three chosen impleentations~\ref{cap:photonic}~\ref{cap:ion}~\ref{cap:superconductor}, as well as the main advantages and disadvantages of each implementation~\ref{sec:comparative}.

@@

  \item \emph{When the physical quantity A is measured on a system in the normalized state \(\ket{\psi}\) the probability \(\mathcal{P}(a_n)\)  of obtaining the eigenvalue \(a_n\) of the corresponding observable A is: \\
          \( \mathcal{P}(a_n) = \sum_{i=1}^{g_n}\ket{\bra{u_n^i}\psi}|^2 \) \\
          where \(g_n\) is the degree of degeneracy of \(a_n\) and \( \{ \ket{u_n^i} \} \) \( (i=1,2,\ldots, g_n) \) is an orthonormal set of vectors in the eigensubspace \(\mathcal{E}_n\) associated with the eigenvalue \(a_n\) of A.}

@@

  \item \emph{The time evolution of the state vector \(|\psi (t)\) is governed by the Schrödinger equation: \\
          \(i\hbar \frac{d}{dt}\ket{\psi(t)} = H(t)\ket{\psi(t)}\) \\
          where \(H(t)\) is observable associated with the total energy of the system.}\label{post:schroedinger}
\end{enumerate}

@@

A notable platform for constructing a multi-qubit quantum processor revolves around superconducting qubits. These qubits employ the quantum degrees of freedom found within nanofabricated, anharmonic oscillators built from superconducting circuit components. Div'rging from alternative platforms, wherein quantum information is encoded within natural microscopic quantum systems, superconducting qubits exhibit a macroscopic scale and are lithographically defined.

@@

To probmote charge and flux to quantum operators, we can use the commutation relation \( [\hat\Phi, \hat Q] = i\hbar \). In a LC circuit, both the capacitor and inductor are linear components, so the Hamiltonian is then given by:
\begin{equation}
  H = 4E_C n^2 = \frac{1}{2}E_L\phi^2
\end{equation}
\noindent where \(\phi = 2\pi\frac{\Phi}{\Phi_0}\) is the reduced flux, \(n = \frac{Q}{2e}\) is the reduced charge, \(E_C = \frac{e^2}{2C}\) is the charging energy, \(E_L = \frac{\Phi_0^2}{4\pi^2L}\) is the inductive energy, and \(\Phi_0 = \frac{h}{2e}\) is the superconducting magnetic flux quantum.

>>>>

\begin{abstract}
  This work aims to explain the physical principles of quantum computers. We will discuss how some physical systems can be used to peform computation, especially with respect to three chosen impleentations, as well as the main advantages and disadvantages of each implementation.
  The implementations we will discuss are ion traps, photonic models and solid state systems. The ion trap model revolves around the manipulation of ions confined within a trap, while the photonic model centers on the manipulation of photons within a cavity, and the solid-state model focuses on the manipulation of electrons within a superconducting circuit.
  The main advantages and disadvantages of each model are presented, as well as the main challenges for the construction of a quantum computer.

@@

In this work we will discuss the physical principles of quantum computers. We will discuss how some physical systems can be used to peform computation~\ref{sec:physical_properties}, especially with respect to three chosen implementations~\ref{cap:photonic}~\ref{cap:ion}~\ref{cap:superconductor}, as well as the main advantages and disadvantages of each implementation~\ref{sec:comparative}.

@@

  \item \emph{When the physical quantity A is measured on a system in the normalized state \(\ket{\psi}\) the probability \(\mathcal{P}(a_n)\)  of obtaining the eigenvalue \(a_n\) of the corresponding observable A is: \\
        \( \mathcal{P}(a_n) = \sum_{i=1}^{g_n}\ket{\bra{u_n^i}\psi}|^2 \) \\
        where \(g_n\) is the degree of degeneracy of \(a_n\) and \( \{ \ket{u_n^i} \}_{i=1}^{g_n} \) is an orthonormal set of vectors in the eigensubspace \(\mathcal{E}_n\) associated with the eigenvalue \(a_n\) of A.}

@@

  \item \emph{The time evolution of the state vector \(\ket{\psi (t)}\) is governed by the Schrödinger equation: \\
          \(i\hbar \frac{d}{dt}\ket{\psi(t)} = H(t)\ket{\psi(t)}\) \\
          where \(H(t)\) is observable associated with the total energy of the system.}\label{post:schroedinger}
\end{enumerate}

@@

A notable platform for constructing a multi-qubit quantum processor revolves around superconducting qubits. These qubits employ the quantum degrees of freedom found within nanofabricated, anharmonic oscillators built from superconducting circuit components. Diverging from alternative platforms, wherein quantum information is encoded within natural microscopic quantum systems, superconducting qubits exhibit a macroscopic scale and are lithographically defined.

@@

To promote charge and flux to quantum operators, we can use the commutation relation \( [\hat\Phi, \hat Q] = i\hbar \). In a LC circuit, both the capacitor and inductor are linear components, so the Hamiltonian is then given by:
\begin{equation}
  H = 4E_C n^2 = \frac{1}{2}E_L\phi^2
\end{equation}
\noindent where \(\phi = 2\pi\frac{\Phi}{\Phi_0}\) is the reduced flux, \(n = \frac{Q}{2e}\) is the reduced charge, \(E_C = \frac{e^2}{2C}\) is the charging energy, \(E_L = \frac{\Phi_0^2}{4\pi^2L}\) is the inductive energy, and \(\Phi_0 = \frac{h}{2e}\) is the superconducting magnetic flux quantum.
